Diagnosis Visualizations

### 2023-06-07 Diagnosis_Vis.Rmd
Got perportions of disorders correct.

@@

@@

tabs<-as.data.frame.matrix(xtabs(~Disorder_treat + Disorder_Present, data = Mothership_current_Imp))

anx<-sum(tabs[1,])
bpd<-sum(tabs[2,])
mood<-sum(tabs[3,])
trauma<-sum(tabs[4,])

tabs[1,] <- (tabs[1,] /anx)*100
tabs[2,] <- (tabs[2,] /bpd)*100
tabs[3,] <- (tabs[3,] /mood)*100
tabs[4,] <- (tabs[4,] /trauma)*100

@@

```{r}
Mothership_current_Imp$Disorder_Present
Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .5)+
  scale_size_area(max_size = 30) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Other_Co" = "Other",
                            "No_Co" = "None",
                            "Mood_C" = "Mood",
                            "BPD_Co_C" = "BPD",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 
```

>>>>

                OCD_P = as.factor(OCD_P),

@@

                BPD_P = as.factor(BPD_P),

@@

tabs<-as.data.frame.matrix(xtabs(~ Disorder_Present + Disorder_treat, data = Mothership_current_Imp))

anx<-summary(Mothership$Anxiety_D)[2]
bpd<-summary(Mothership$BPD_P)[2]
mood<-summary(Mothership$Mood_D)[2]
trauma<-summary(Mothership$Trauma_D)[2]

tabs[,1] <- (tabs[,1] / anx)*100
tabs[,2] <- (tabs[,2] /bpd)*100
tabs[,3] <- (tabs[,3] /mood)*100
tabs[,4] <- (tabs[,4] /trauma)*100

@@

```{r}
Mothership_current_Imp$Disorder_Present
CO_OC<- Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .5)+
  scale_size_area(max_size = 30) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Other_Co" = "Other",
                            "No_Co" = "None",
                            "Mood_C" = "Mood",
                            "BPD_Co_C" = "BPD",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis")

CO_OC
```
